\textbf{INSERT TITLE HERE}

### 2013-11-16 LaTeX/paper.tex
added stuff about catastrophic cover

\subsection{Catastrophic Cover}

>>>>

\subsection{Catastrophic Cover}
In a localized catastrophic event such as those that happened on September 11, 2001, there will be
many casualties in a single location that require aid. Ambulances, and other emergency vehicles,
such as police cars and fire trucks, will need to respond quickly in order to aid the most critically
injured first, who will be sorted by triage. Therefore, it is very important for ambulances to be able to
reach the emergency as quickly as possible, regardless of the initial location of the ambulances and the
location of the emergency.

Catastrophic events will cause more casualties than emergency personnel will be able to service, so as a result,
ambulances will have to act as shuttles to hospitals for the injured. Therefore, to maximize throughput
cities should arrange hospitals to minimize the average time between all areas and the nearest
hospital.

Since metropolitan areas are most likely to be affected by catastrophic events, and catastrophic events there
will affect significantly more people, to maximize patient throughput cities should arrange hospitals to minimize
the average time between all areas and the nearest hospital. Futhermore, due to differences in population density,
statistically, an accident in a metropolitan area will demand more urgent care than a similar accident
in a rural or suburban area. Therefore, when the city lays out its stations for ambulances, attempting to minimize
travel times to any area, it should put significantly more weight on minimizing travel time to metropolitan areas.
